The Fates of Merging Supermassive Black Holes and a Proposal for a New Class of X-Ray Sources

### 2020-08-09 paper.tex
Added back bolding to highlight changes from previous version, as per MNRAS instructions

Orbiting black holes have been studied in the past using both semi-analytical methods and dynamical simulations.  \citet{2003ApJ...582..559V} followed the merger history of dark matter haloes and associated BH mergers using Monte-Carlo realizations, and found a population of BHs orbiting in galaxy haloes and the intergalactic medium at the present epoch.  In a follow-up study, \citet{2005MNRAS.358..913V} found that the orbiting black holes should have luminosities in X-ray $\lessapprox10^9 M_{\sun}$.  \citet{2008MNRAS.390.1311B} looked at the effects of gravitational recoil due to BH mergers on the growth of SMBHs, and found that the recoiled BHs can orbit their host galaxy for $10^6-10^9$ years before returning to the center, while accreting gas equivalent to approximate $10{\%}$ of their initial mass.  \citet{2017MNRAS.472.1526C} simulated recoiling black hole trajectories, altering various parameters in their simulations and observing the effects on escape velocities.  They found that the overall mass of the host halo and the accretion rate onto the halo are the largest factors affecting the escape velocity of a recoiled BH.  In a large-scale cosomological simulation (ROMULUS25) of Milky Way-mass galaxies, \citet{2018ApJ...857L..22T} found that such haloes would have approximately 5 SMBHs within $10kpc$ from the galactic center, and 12 SMBHs within they virial radius.  \citet{2020MNRAS.495.4681I} used a semi-analytical model to study the mass assembly and spin evolution of SMBHs, as well as the effects of gravitational recoil on central and orbiting black holes.  One of their findings is that the number and masses of orbiting black holes corresponds with the halo and stellar mass of the host galaxy, with their location within the galaxy being approximately $0.5R_{200}$.

@@

\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.  In their simulations, they seed a black hole in any galaxy that reaches their prescribed lower mass limit ($M_* \simeq 10^8 M_{\sun}$).  The initial mass of the seeded black hole is then taken to be $nM_{*, bulge}$, where $n$ is drawn from a log-normal distribution with median $\simeq10^{-3}$ and intrinsic scatter of 0.35.  The black holes subsequently grow through BH-BH mergers and gas accretion.  The accretion component is proportional to the stellar mass formed in the host galaxy in a given redshift slice times the bulge fraction of the host galaxy.  They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.  They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citealt{2012MNRAS.423.1992S, 2013MNRAS.428.1351G, 2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.

\citet{2015ApJ...799..178K} also had a prescription for re-seeding a galaxy with a central black hole in the event the previous one was ejected due to gravitational recoils. If the galaxy subsequently produced an additional $10^9M_{\sun}$ in unscaled galactic stellar mass, they re-seed the galaxy using the same method described above.  In our simulations, the central black holes were never ejected, and we did not need to use the above-described re-seeding.

The primary data we extracted from the above work was organized as follows:
\begin{itemize}
    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4\geq z \geq0$. The original \citet{2015ApJ...799..178K} simulations had 38 redshift slices.  However, one was dropped due to an error in the dataset.
    \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
\end{itemize}

@@

The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.  Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0.  In considering time and resources, we chose the 11 galaxies that had the largest number of black holes to run the simulations.  The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.

@@

Figure \ref{fig:stellar1} is a partial, approximate, replication of Figure 11 from \citet{2018AstL...44....8K} (abundance matching line).  We rescaled our stellar masses at $z=0$ by using a lognormal distribution.  For a given galaxy's dark matter mass, the mean of the distribution, $\mu$, was taken to be the point on the abundance matching line at that dark matter mass.  The standard deviation was assumed arbitrarily to be $0.3\mu$.  After rescaling the stellar masses at $z=0$, we used that proportionality to rescale the masses through the entire simulation from $4\geq z \geq0$.  Table \ref{table:gal_char} shows the original and rescaled stellar masses.

@@

where $\Delta v_\parallel \equiv \Delta \vec{v}\cdot\vec{v}/v$ is the velocity change in direction of motion, and $\Delta \vec{v}_\bot \equiv \Delta \vec{v} - \Delta v_\parallel \cdot\vec{v}/v$ is the velocity change perpendicular to the direction of motion. Here, $\sigma$ is the local velocity dispersion of the host galaxy, $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$. The function $f(\chi)$ is given by 

@@

\subsubsection{Gravitational wave recoils and escape}
The code \textsc{AR-Chain} (\citet{2006MNRAS.372..219M} and \citet{2008AJ....135.2398M}) includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils (\citet{2007ApJ...659L...5C}, \citet{2011PhRvD..83b4003L}, \citet{2013PhRvD..87h4027L}, \citet{2012ApJ...744...45B}) following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than four times the Schwarzschild radius of the more massive black hole.  At the moment of the merger, we also assume that the spin vectors of the two SMBHs are randomly aligned.  There are reasons to believe that the actual spins of the binary BHs may not be randomly aligned, as described further below.

A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum.  This kick can result in velocities of the merged binary from approximately $200-5000\ km\ s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}).  In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.  As mentioned above, we calculate the spins and kicks (recoil velocities) of the black holes in the same way that \citet{2015ApJ...799..178K} implemented it (their Equations 11), which in turn followed the implementation from \citet{2012PhRvD..85h4015L}.  We also adopt a value of $\xi$ = 145$^{\circ}$ based on the numerical results for quasi-circular merger configurations from \citet{2008PhRvD..77d4028L}.

The kick distribution is approximated in the way described above, but the actual distribution of kicks may vary since, for example, the alignment of BH spins may not be fully random, as demonstrated in \citet{2012PhRvD..85h4015L} and \citet{2010MNRAS.402..682D}. Accretion disks surrounding the merging black holes may help align spins between the merging black holes on a timescale shorter than the time needed to merge.

@@

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined by the Chandrasekhar formula from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The formula above was not a factor during the simulations.  We used the full dynamical friction model (section \ref{psd}) during the simulations.  The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be the circular velocity at that radius, $v_c = \sqrt{GM(R_e)/R_e}$, with orientation, $v_x$, $v_y$, and $v_z$, randomly chosen.

@@

In this section, "orbiting" black holes refer to all black holes that are still orbiting within their host galaxy at $z=0$.  "Kicked" black holes are a subset of orbiting black holes, in that they are still orbiting within their host galaxy, but at some point during the simulation were kicked to a higher orbit due to three-body scattering.  "Ejected" black holes are those that were given a large enough of a recoil velocity due to three-body scattering that they were ejected from their host galaxy.  To clarify, any discussion of kicked black holes below only refers to those that are still orbiting their host galaxy.  Similarly, discussions of ejected black holes only refer to those that were ejected.

@@

\subsection{Mergers}\label{sec:mergers}
The tendency of larger mass black holes to merge with their host can perhaps be more clearly seen by looking at the merger mass ratio between the incoming black hole and the host.  Figure \ref{fig:q_merge_fraction} displays the fraction of galaxy mergers that result in black hole mergers versus the merger mass ratio, defined as $m_2/m_1$, where $m_2$ is the orbiting black hole and $m_1$ is the host black hole.  The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio greater than $10^{-1}$ resulted in the orbiting black hole merging with the host.  It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.  This conclusion is identical to that reached by the careful treatment by \citet{2018MNRAS.473.3410R} (''Interactions between multiple supermassive black holes in galactic nuclei: a solution to the final parsec problem'').

@@

Figure \ref{fig:mvr} is a realization of the final radii of the remaining orbiting black holes at $z=0$.  There is a slight inverse relationship between black hole mass and final radius (solid line), but with a wide dispersion.  It is also evident from the plot that all but two of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$ (which never exceeded 1 kpc in any of the galaxies).  The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.  Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/Final_Radius_v_Mass_of_Orbiting_BHs.png}
\caption{Final radii of remaining orbital black holes at z=0.  Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.  There is a slight inverse relationship between BH mass and final distance from center (solid line).}
\label{fig:mvr}
\end{center}
\end{figure}

@@

Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}\,\text{erg s}^{-1}$ and standard deviation $\sigma=4.5\times10^{3}\,\text{erg s}^{-1}$.
\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/Final_Luminosities_using_Kohei_factor.png}
\caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes, with the lower limit being approximately $10^{38}\;\text{erg}\;\text{s}^{-1}$ (\citet{2018ApJ...862...73L}). The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
\label{fig:ldobhs}
\end{center}
\end{figure}

@@

\citet{guo2020hunting} have shown that there is an additional way of detecting the predicted orbiting massive black holes. They compute that the spectra have a peak at the millimeter wave band, and should enable detectors such as the Atacama Large Millimeter/submillimeter Array (ALMA) and upcoming next generation Very Large Array (ngVLA) to find orbiting black holes with masses down to approximately $M_{\bullet}\simeq2\times10^7 M_{\odot}$ in nearby galaxies such as M87, and $M_{\bullet}\simeq10^5 M_{\odot}$ in the Milky Way.

>>>>

\textbf{Orbiting black holes have been studied in the past using both semi-analytical methods and dynamical simulations.  \citet{2003ApJ...582..559V} followed the merger history of dark matter haloes and associated BH mergers using Monte-Carlo realizations, and found a population of BHs orbiting in galaxy haloes and the intergalactic medium at the present epoch.  In a follow-up study, \citet{2005MNRAS.358..913V} found that the orbiting black holes should have luminosities in X-ray $\lessapprox10^9 M_{\sun}$.  \citet{2008MNRAS.390.1311B} looked at the effects of gravitational recoil due to BH mergers on the growth of SMBHs, and found that the recoiled BHs can orbit their host galaxy for $10^6-10^9$ years before returning to the center, while accreting gas equivalent to approximate $10{\%}$ of their initial mass.  \citet{2017MNRAS.472.1526C} simulated recoiling black hole trajectories, altering various parameters in their simulations and observing the effects on escape velocities.  They found that the overall mass of the host halo and the accretion rate onto the halo are the largest factors affecting the escape velocity of a recoiled BH.  In a large-scale cosomological simulation (ROMULUS25) of Milky Way-mass galaxies, \citet{2018ApJ...857L..22T} found that such haloes would have approximately 5 SMBHs within $10kpc$ from the galactic center, and 12 SMBHs within they virial radius.  \citet{2020MNRAS.495.4681I} used a semi-analytical model to study the mass assembly and spin evolution of SMBHs, as well as the effects of gravitational recoil on central and orbiting black holes.  One of their findings is that the number and masses of orbiting black holes corresponds with the halo and stellar mass of the host galaxy, with their location within the galaxy being approximately $0.5R_{200}$.}

@@

\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.  \textbf{In their simulations, they seed a black hole in any galaxy that reaches their prescribed lower mass limit ($M_* \simeq 10^8 M_{\sun}$).  The initial mass of the seeded black hole is then taken to be $nM_{*, bulge}$, where $n$ is drawn from a log-normal distribution with median $\simeq10^{-3}$ and intrinsic scatter of 0.35.  The black holes subsequently grow through BH-BH mergers and gas accretion.  The accretion component is proportional to the stellar mass formed in the host galaxy in a given redshift slice times the bulge fraction of the host galaxy.}  They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.  They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citealt{2012MNRAS.423.1992S, 2013MNRAS.428.1351G, 2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.

\textbf{\citet{2015ApJ...799..178K} also had a prescription for re-seeding a galaxy with a central black hole in the event the previous one was ejected due to gravitational recoils. If the galaxy subsequently produced an additional $10^9M_{\sun}$ in unscaled galactic stellar mass, they re-seed the galaxy using the same method described above.  In our simulations, the central black holes were never ejected, and we did not need to use the above-described re-seeding.}

The primary data we extracted from the above work was organized as follows:
\begin{itemize}
    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4\geq z \geq0$. \textbf{The original \citet{2015ApJ...799..178K} simulations had 38 redshift slices.  However, one was dropped due to an error in the dataset.}
    \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
\end{itemize}

@@

\textbf{The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.  Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0}.  In considering time and resources, we chose the 11 galaxies that had the largest number of black holes to run the simulations.  The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.

@@

Figure \ref{fig:stellar1} is a partial, approximate, replication of Figure 11 from \citet{2018AstL...44....8K} (abundance matching line).  We rescaled our stellar masses at $z=0$ by using a lognormal distribution.  For a given galaxy's dark matter mass, the mean of the distribution, $\mu$, was taken to be the point on the abundance matching line at that dark matter mass.  The standard deviation was assumed arbitrarily to be $0.3\mu$.  \textbf{After rescaling the stellar masses at $z=0$, we used that proportionality to rescale the masses through the entire simulation from $4\geq z \geq0$.}  Table \ref{table:gal_char} shows the original and rescaled stellar masses.

@@

where $\Delta v_\parallel \equiv \Delta \vec{v}\cdot\vec{v}/v$ is the velocity change in direction of motion, and $\Delta \vec{v}_\bot \equiv \Delta \vec{v} - \Delta v_\parallel \cdot\vec{v}/v$ is the velocity change perpendicular to the direction of motion. Here, \textbf{$\sigma$ is the local velocity dispersion of the host galaxy,} $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$. The function $f(\chi)$ is given by 

@@

\subsubsection{Gravitational wave recoils and escape}
The code \textsc{AR-Chain} (\citet{2006MNRAS.372..219M} and \citet{2008AJ....135.2398M}) includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils (\citet{2007ApJ...659L...5C}, \citet{2011PhRvD..83b4003L}, \citet{2013PhRvD..87h4027L}, \citet{2012ApJ...744...45B}) following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than four times the Schwarzschild radius of the more massive black hole.  At the moment of the merger, we also assume that the spin vectors of the two SMBHs are randomly aligned.  \textbf{There are reasons to believe that the actual spins of the binary BHs may not be randomly aligned, as described further below.}

A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum.  This kick can result in velocities of the merged binary from approximately $200-5000\ km\ s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}).  In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.  \textbf{As mentioned above, we calculate the spins and kicks (recoil velocities) of the black holes in the same way that \citet{2015ApJ...799..178K} implemented it (their Equations 11), which in turn followed the implementation from \citet{2012PhRvD..85h4015L}.  We also adopt a value of $\xi$ = 145$^{\circ}$ based on the numerical results for quasi-circular merger configurations from \citet{2008PhRvD..77d4028L}.}

\textbf{The kick distribution is approximated in the way described above, but the actual distribution of kicks may vary since, for example, the alignment of BH spins may not be fully random, as demonstrated in \citet{2012PhRvD..85h4015L} and \citet{2010MNRAS.402..682D}. Accretion disks surrounding the merging black holes may help align spins between the merging black holes on a timescale shorter than the time needed to merge.}

@@

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined by the Chandrasekhar formula from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
\textbf{The formula above was not a factor during the simulations.  We used the full dynamical friction model (section \ref{psd}) during the simulations}.  The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be the circular velocity at that radius, $v_c = \sqrt{GM(R_e)/R_e}$, with orientation, $v_x$, $v_y$, and $v_z$, randomly chosen.

@@

\textbf{In this section, "orbiting" black holes refer to all black holes that are still orbiting within their host galaxy at $z=0$.  "Kicked" black holes are a subset of orbiting black holes, in that they are still orbiting within their host galaxy, but at some point during the simulation were kicked to a higher orbit due to three-body scattering.  "Ejected" black holes are those that were given a large enough of a recoil velocity due to three-body scattering that they were ejected from their host galaxy.  To clarify, any discussion of kicked black holes below only refers to those that are still orbiting their host galaxy.  Similarly, discussions of ejected black holes only refer to those that were ejected.}

@@

\subsection{Mergers}\label{sec:mergers}
The tendency of larger mass black holes to merge with their host can perhaps be more clearly seen by looking at the merger mass ratio between the incoming black hole and the host.  Figure \ref{fig:q_merge_fraction} displays the fraction of galaxy mergers that result in black hole mergers versus the merger mass ratio, defined as $m_2/m_1$, where $m_2$ is the orbiting black hole and $m_1$ is the host black hole.  The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio greater than $10^{-1}$ resulted in the orbiting black hole merging with the host.  \textbf{It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.  This conclusion is identical to that reached by the careful treatment by \citet{2018MNRAS.473.3410R} (''Interactions between multiple supermassive black holes in galactic nuclei: a solution to the final parsec problem'').}

@@

Figure \ref{fig:mvr} is a realization of the final radii of the remaining orbiting black holes at $z=0$.  There is a slight inverse relationship between black hole mass and final radius (solid line), but with a wide dispersion.  It is also evident from the plot that all but two of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$ (which never exceeded 1 kpc in any of the galaxies).  \textbf{The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.  Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/Final_Radius_v_Mass_of_Orbiting_BHs.png}
\caption{Final radii of remaining orbital black holes at z=0.  \textbf{Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center}.  There is a slight inverse relationship between BH mass and final distance from center (solid line).}
\label{fig:mvr}
\end{center}
\end{figure}

@@

Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}\,\text{erg s}^{-1}$ and standard deviation $\sigma=4.5\times10^{3}\,\text{erg s}^{-1}$.
\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/Final_Luminosities_using_Kohei_factor.png}
\caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes, \textbf{with the lower limit being approximately $10^{38}\;\text{erg}\;\text{s}^{-1}$ (\citet{2018ApJ...862...73L})}. The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
\label{fig:ldobhs}
\end{center}
\end{figure}

@@

\textbf{\citet{guo2020hunting} have shown that there is an additional way of detecting the predicted orbiting massive black holes. They compute that the spectra have a peak at the millimeter wave band, and should enable detectors such as the Atacama Large Millimeter/submillimeter Array (ALMA) and upcoming next generation Very Large Array (ngVLA) to find orbiting black holes with masses down to approximately $M_{\bullet}\simeq2\times10^7 M_{\odot}$ in nearby galaxies such as M87, and $M_{\bullet}\simeq10^5 M_{\odot}$ in the Milky Way.}
